\LARGE \bf Optimal Joint Probabilistic Data Association Filter\\ Avoiding Coalescence in Close Proximity

### 2018-06-09 Conference/ECC 2014/ECC14__Final.tex
added Conference folder

\title{\LARGE \bf
%Recursive Kalman-Mahanobis JPDAF Minimization to avoid Coalescence of Estimates in Close Proximity
Optimal Joint Probabilistic Data Association Filter\\ Avoiding Coalescence in Close Proximity }
\author{Evan Kaufman and Taeyoung Lee$^*$
 \thanks{Evan Kaufman and Taeyoung Lee are with Department of Aerospace Engineering, George Washington University, Washington, DC. Email: {\tt\footnotesize \{evankaufman, tylee\}@gwu.edu }}
\thanks{$^*$This research has been supported in part by NSF under the grants CMMI-1243000 (transferred from 1029551), CMMI-1335008, and CNS-1337722.}}

@@

\begin{abstract}
This paper deals with an estimation problem where a known number of targets in close proximity are observed but the measurement originations are uncertain. It is well known that joint probabilistic data association filters (JPDAF) are effective in handing uncertain measurement originations with clutter, but they are prone to estimation coalescence, particularly when close neighboring targets share measurements. This paper proposes a Coalescence Avoiding Optimal JPDAF (C-JPDAF) that minimizes the weighted sum of the posterior uncertainty and a measure of similarity between estimated probability densities. The proposed approach has simpler structures than other coalescence avoiding approaches based on pruning, while exhibiting excellent filtering performance for targets in close proximity with crossing tracks. These are illustrated by a numerical example of two satellites on crossing orbits around the Earth.
%The algorithm is derived and explained, involving a higher computational cost that the JPDAF, but not high enough to prevent the possibility real-time implementation. A numerical example demonstrates how the C-JPDAF is able to maintain the correct trajectories of slowly crossing estimates whereas the JPDAF is not. The results show that the Kalman gain is an effective initial guess for the C-JPDAF, and we discuss the circumstances that warrant the algorithm's use.
\end{abstract}

@@

Data association is a heavily studied field with many applications in estimation when measurements are not necessarily originating from a single target.
We consider applications wherein multiple targets of interest enter the field of view of a sensor; however, the measurement origin is unknown.
To properly track these targets, we require estimation techniques to associate targets with measurements.
When the targets are in very close proximity, the association uncertainty grows, and an effective algorithm is necessary to maintain close estimations of the targets.

A variety of data association techniques are considered for close-proximity trajectories with varying performance.
Some approaches such as multiple hypothesis tracking (MHT) and probability hypothesis density (PHD) techniques involve a high computational load, especially when targets are in close proximity, making real-time implementation more difficult~\cite{MHT1},~\cite{PHD1}, and~\cite{PHD2}.
Many other techniques may involve the Kalman filter (KF) or extended KF (EKF), which are well studied and provide a framework for recursive data association techniques that are much easier to implement in real-time.
A common heuristic approach is known as the nearest neighbor filter (NNF), which is a simple algorithm that only updates estimates for measurements with the closest square Mahalnobis distance, updating other targets only with their predictions~\cite{NN2}.
This is considered a \emph{hard decision} in~\cite{JPDAF1}, or that every measurement update receives full weighting; if the decision is incorrect, these measurement updates can result in detrimental effects to the associations of the estimates, so this technique is avoided in the analysis of this paper.
Alternatively, some approaches calculate the minimum mean square error (MMSE) of the estimates and their associated uncertainty.
The probabilistic data association (PDA) technique is effective in tracking a single target because it updates with a \emph{soft decision}; in particular, this approach updates provides a weighting from a likelihood of measurement association.

The joint PDA (JPDA) is an extension of the PDA to incorporate multiple targets~\cite{JPDAF1},~\cite{TrackDataAssoc}.
The JPDA filter (JPDAF) is particularly advantageous in multi-target scenarios because when targets share measurements, the soft decisions prevent loss of information, which occurs with hard decisions.
However, when neighboring targets share measurements, the estimates are subject to coalescence.

@@

% Old introduction:

%\section{Introduction}
%Data association has been widely studied with various applications in estimation of a single or multiple targets with measurements that are not necessarily originating from correct targets in order. To properly track multiple targets with measurement origin uncertainties, measured data should be properly associated to targets with certain probabilities. %When the targets are in very close proximity, the association uncertainty grows, and an effective algorithm is required to maintain close estimations of the targets. Otherwise, estimators tend to coalesce neighboring tracks. 
%%This paper considers estimation wherein multiple targets of interest enter the field of view of a sensor; however, the measurement origin is unknown. 
%A variety of data association techniques with varying performance have been studied. A common heuristic approach is known as the nearest neighbor filter (NNF), where measurements with the closest distance are only applied~\cite{NN2}. This is considered a \emph{hard decision} in~\cite{JPDAF1}, as every selected measurement update receives full weighting. Therefore, if the decision is incorrect, these measurement updates can result in detrimental effects to the associations of the estimates.  Alternatively, there are approaches that calculate the minimum mean square error (MMSE) of the estimates and their associated uncertainty. The probabilistic data association (PDA) technique is effective in tracking a single target because it updates with a \emph{soft decision}; in particular, this approach updates provides a weighting from a likelihood of measurement association. Other approaches include multiple hypothesis tracking (MHT) and probability hypothesis density (PHD) techniques~\cite{MHT1,PHD1,PHD2}. 
%%Many other techniques may involve the Kalman filter (KF) or extended KF (EKF), which are well studied and provide a framework for recursive data association techniques that are much easier to implement in real-time.
%The joint PDA (JPDA) is an extension of the PDA to incorporate multiple targets~\cite{JPDAF1},~\cite{TrackDataAssoc}.
%The JPDA filter (JPDAF) is particularly advantageous in multi-target scenarios because when targets share measurements, the soft decisions prevent loss of information that occurs with hard decisions. As such, it is well known that JPDAF are effective in handling data clutter or missed detection. However, when the targets are in very close proximity, the association uncertainty grows significantly, thereby degrading the filtering performance. Furthermore, the estimated probability distributions tend to be coalesced especially if the paths of neighboring targets cross with each other. 
%%neighboring targets share measurements, the estimates are subject to coalescence.
%Many techniques to avoid track coalescence involve the concept that when the exact nearest neighbor probabilistic data association (ENNPDA) is applied, which associates a measurement with a strong decision to the most likely estimate, the estimates are insensitive to track coalescence~\cite{Coal1}. By pruning the tracks, or designing a set of rules to determine high likelihood scenarios, an algorithm choice or weighing scheme is applied to the measurement updates.
%For example in~\cite{Fitzgerald}, the algorithm involves a set of rules based on the data received with respect to the estimates. A special logic is introduced that determines how weighting of the updates is defined or if a new track should be considered. In some cases, it is possible for an incorrectly associated estimate measurement may receive full weighting in the update. Other criteria or extensions of this approach are detailed in~\cite{Coal_d},~\cite{Coal_e}, and~\cite{Coal_c}, which can be very effective, but information may be lost when measurements are omitted from updating an estimates with small probabilities of association because the pruning rule prevented these association possibilities.
%This paper is focused on optimal joint probabilistic data association filter that avoids coalescence in close proximity. We propose a novel approach to remove coalescence by minimizing a similarity index of the estimates. More explicitly, the gain of the proposed estimator is chosen such that a weighted sum of the size of uncertainties and a similarity measure between estimated states is minimized at each update. This yields an optimal recursive estimation algorithm that compensates for the effects of coalescence systematically. The proposed approach has simpler structures compared with pruning-based approaches, and it is computationally efficient. As it is still based on probabilistic data association, it avoids the heuristic nature, loss of information, or the risk of other coalescence avoidance approaches based on hard-decision.
%The paper is organized as follows: the dynamics of target and the measurement models are described in Section \ref{ProbDef}. The proposed Coalescence Avoiding Optimal JPDAF (C-JPDAF) are presented at Sections \ref{JPDAF}, and the optimal gain that minimizes a weighted cost of uncertainty and similarity is derived in Section \ref{C-JPDAF}.
%These are illustrated by a numerical example for estimating two satellites in crossing orbits in Section \ref{NumRes}, followed by conclusions in Section \ref{ConclusionFutureWork}.

@@

This section describes the dynamics of targets and the measurement model considered in this paper, and a filtering problem is formulated.

% Equations of motion
\subsection{Dynamics of Targets and Measurements}

The dynamics of each target is modeled as a linear stochastic discrete-time system. The equations of motion for the $i$-th system are described by
\begin{align}
x_{i_{k+1}} & = A_{i_k} x_{i_k} + w_{i_k},\label{eqn:xkp}\\
z_{i_k} & = H_{i_k} x_{i_k} + v_{i_k},
\end{align}
where $x_{i_k}\in\Re^n$ is the state vector, $z_{i_k}\in\Re^m$ is the output vector, and  the matrices $A_{i_k}\in\Re^{n\times n}$ and $H_{i_k}\in\Re^{m\times n}$ describe system dynamics and outputs. The process noise and the measurement noise are denoted by $w_{i_k}\in\Re^n$ and $v_{i_k}\in\Re^m$, respectively, and it is assumed that they are zero-mean, mutually independent white, Gaussian noise sequences with known covariance matrices $Q_{i_k}\in\Re^{n\times n}$ and $R_{i_k}\in\Re^{m\times m}$, respectively, i.e.,
\begin{align}
w_{i_k} \sim \mathcal{N}[0,Q_{i_k}],\quad
v_{i_k} \sim \mathcal{N}[0,R_{i_k}].
\end{align}

@@

To demonstrate the main idea of the proposed data association filter concisely, it is assumed that there are two targets, i.e., $i\in\{1,2\}$. But, the results of this paper are readily generalized to arbitrary number of systems provided the number of targets is known.

@@

The following assumptions are made on the measurement origination, considering the case where two target are in close proximity. First, it is assumed that there is only a single measurement at each time in the region of close proximity. Secondly, we assume that this measurement originates from either one of the targets and it is not from other sources such as clutter. Also, the case when neither target is measured is not considered. Like the JPDA, all targets are assumed to fall inside the validation gate. The measurement origination between targets is random, unknown, and equally likely.

More explicitly, let $\Theta_i$ be the event that the measurement originates from the $i$-th target, for $i\in\{1,2\}$. According to the above assumptions, we have
\begin{align}
P(\Theta_1\cup \Theta_2)&=1,\quad
P(\Theta_1\cap \Theta_2)=0,\\
P(\Theta_1)&=P(\Theta_2)=0.5.\label{eqn:MeaOrig}
\end{align}

%\EditTL{
%The only source of knowledge to associate data at time $k$ is the measurement $z_k$.
%Using the estimate prediction $\hat x^-$, we define its prediction
%\begin{align}
%z_{i_{k|k-1}}=H_{i_k}\hat x_{i_k}^-
%\end{align}
%which is used to determine the innovation
%\begin{align}
%e_{i_k}=z_k-z_{i_{k|k-1}}
%\end{align}
%and its covariance
%\begin{align}
%S_{i_k}=H_{i_k}P_{i_k}^{-}H_{i_k}^T+R_{i_k}
%\end{align}
%which is used to determine the weighting of the measurement update.
%
%We can modify JPDAF weighting and update from~\cite{JPDAF1} and~\cite{TrackDataAssoc}.
%The assumptions in this section are applied and significantly simplify the weighting calculation. For the $i$-th target, the weighting $\beta_i$ is reduced to (see proof in the appendix)
%\begin{gather}
%\beta_{i_k}=\frac{f_{i_k}}{\displaystyle\sum\limits_{y=1}^2 f_{y_k}} \\
%f_{y_k}=\mathcal{N}[z_{k};\hat z_{i_{k|k-1}},S_{i_k}].
%\end{gather}
%where $\mathcal{N}[x;\mu,\Sigma]$ is the Gaussian probability density function of mean $\mu$ and covariance matrix $\Sigma$ evaluated at $x$.}

@@

A filtering problem is formulated as recursively updating the estimated state of each target and its covariance, namely $(\hat x_{i_k}, P_{i_k})$ based on the above assumptions given by \refeqn{xkp}--\refeqn{MeaOrig}. In particular, we wish to avoid track coalescence when two targets are in close proximity.

%The filtering problem involves updating each state using this weighting. We wish to update the estimates of both systems on parallel filters; however, when these weightings are close, multiple estimates share a single measurement, causing the estimates to coalesce, which we wish to avoid.

% Association Problem

	% Assumptions on measurement
		% only one measurement is available at each time 
		% the case of no measurement is not included
		% measurement origination is random and unknown
		% these assumptions represent two targets in close proximity, such as crossing targets

	% Data association event
		% there are only two events for data association
		% data association probability (beta) is defined as...
		% (Proper justification is needed, as this is one of the key assumptions)

	% Filtering problem
		% We wish to estimate states of both system

@@

Joint probabilistic data association filter is a suboptimal Bayesian filter for multiple targets where the probabilities of association are computed for the latest set of measurements only~\cite{TrackDataAssoc}. This section summarizes the approaches of JPDAF.

\subsection{Flow Update}
Similar to Kalman filters, the JPDAF is composed of a flow update and a measurement update. During the flow update (or prediction step), the estimated state $\hat x_{i_k}$ and its covariance $P_{i_k}$ of each target are updated as in the standard filter as follows:
\begin{gather}
\hat x_{i_{k}} = A_{i_{k-1}} \hat x_{i_{k-1}},\\
P_{i_{k}} = A_{i_{k-1}} P_{i_{k-1}} A_{i_{k-1}}^T + Q_{i_{k-1}}.
\end{gather}
These are initialized by \refeqn{xi0}, and they are repeated between measurements.

@@

Next, we consider the measurement update step. Let  the priori value of a variable and its posteriori value be denoted by the superscript $-$ and $+$, respectively. For a given measurement $z_{k}$, its measurement residual or innovation for the $i$-th target is given by
\begin{align*}
e_{i_k} = z_k - z_{i_{k|k-1}},
\end{align*}
where $z_{i_{k|k-1}}$ is the predicted measurement given by
\begin{align}
z_{i_{k|k-1}} = H_{i_k} \hat x_{i_k}^-.
\end{align}
The innovation covariance $S_{i_k}$ is
\begin{align}
S_{i_k}=H_{i_k}P_{i_k}^{-}H_{i_k}^T+R_{i_k}.
\end{align}

@@

The resulting posteriori covariance is given by
\begin{align}
\label{KalCov}
%P^+_{i_k}=&P^-_{i_k}-\beta_{i_k}K_{i_k}S_{i_k}K_{i_k}^T.
P^+_{i_k}=&P^-_{i_k}-\beta_i[K_iH_iP_i^-+P_i^-H_i^TK_i^T-K_iS_{i_k}K_i^T].
\end{align}
(see Appendix for derivation of (\ref{KalCov})).

@@

The joint probabilistic data association filter described in the previous section is effective in handling clutter or missed detection of multiple targets. However, it is prone to coalescing estimates, especially with targets in close-proximity. Here, we present a coalescence-avoiding optimal JPDAF, hereafter C-JPDAF for short, to avoid coalescence of the estimates. The main idea is choosing the estimator gain such that a weighted sum of the size of uncertainty and a measure of similarity is minimized.

@@

For two probability density functions, $f_1(x)$ and $f_2(x)$, Matusita's measure is defined as
\begin{align*}
\zeta = \int \sqrt{f_1(x)f_2(x) dx},
\end{align*}
which is between 0 and 1, and it measures the similarity between two densities~\cite{Coal_k}.

Using the fact that the posteriori states $\hat x_1^+$ and $\hat x_2^+$ are Gaussian, Matusita's measure between two targets can be written as
\begin{align}
\zeta=\zeta_1\zeta_2,
\end{align}
where
\begin{align}
\label{Q}
\zeta_1=&\frac{2^\frac{n}{2}|P_1^+|^{\frac{1}{4}}|P_2^+|^{\frac{1}{4}}}{|P_1^++P_2^+|^{\frac{1}{2}}},\\
\label{R}
\zeta_2=&\exp{\left\{-\frac{1}{4}(\hat x^+_1-\hat x^+_2)^T(P_1^++P_2^+)^{-1}(\hat x^+_1-\hat x^+_2)\right\}}.
\end{align}
Here $\zeta_1$ measures the differences in the covariance matrices and $\zeta_2$ represents the spread in the means.
	% Introduce the definition of M-measure
	% Introduce the definition of Bhattacharyya distance

@@

\begin{figure}
\setlength{\unitlength}{0.1\columnwidth}
\centerline{\footnotesize\selectfont
\begin{picture}(8.5,7.3)(-0.5,-0.8)
\put(-0.5,3){\rotatebox{90}{Cost}}
\put(0,0){\includegraphics[width=0.8\columnwidth]{ECC14_fig1.pdf}}
\put(6.2,0.2){\shortstack[c]{Uncertainty\\ cost: $J_P$}}
\put(6.2,2.8){\shortstack[c]{Similarity\\ cost: $J_S$}}
\put(5.7,5.2){\shortstack[c]{Weighted sum:\\ $J=J_P+cJ_S$}}
\put(4.98,0.78){\circle*{0.1}}
\put(2.48,1.57){\circle*{0.1}}
\put(5.0,-0.3){$K_{JPDA}$}
\put(2.5,-0.3){$K$}
\put(3.1,-0.8){Estimator gain}
\end{picture}
}
\caption{Illustration of optimal coalescence avoidance: several costs are illustrated with respect to the estimator gain $K$ (red: uncertainty cost $J_P$, blue: similarity cost $J_S$, black: weighted sum). The estimator gain $K_{JPDA}$ of JPDA is selected to minimize the uncertainty cost. In the proposed approach, the estimator gain $K$ is chosen such that the weighted sum of the uncertainty cost and the similarity cost is minimized. In short, at the expense of increased uncertainty at a single step, the proposed approach prevents coalescence. The increased uncertainty at each step is rewarded by reducing the overall estimation error drastically by maintaining correct data association throughout crossing tracks in close proximity.}
%The cost functions of target 1 are examined under the variation of a single element of $K_1$. The resulting cost function (black) is minimized slightly to the right of the uncertainty cost function (blue). Note that the total cost when the Kalman gain is applied does not lie on the total cost curve because other elements of this gain that are not optimal. In Kalman filtering applications, including the JPDAF, only the uncertainty cost function is minimized.}
\label{CostTrends}
\end{figure}

More explicitly, the uncertainty cost $J_P$ is defined as the sum of the trace of each posteriori covariance:
\begin{align}
J_P=\tr{P^+_1}+\tr{P^+_2},\label{eqn:JP}
\end{align}
where $P^+_{i_k}$ is obtained by (\ref{KalCov}). The similarity cost is chosen as the second part of the Matusita's measure that represent the weighted-spread of the mean values:
\begin{align}
J_S&=\exp (-au),\\
u & = (\hat x^+_1-\hat x^+_2)^T(P^+_{1}+P^+_{2})^{-1}(\hat x^+_1-\hat x^+_2).\label{eqn:u}
\end{align}
for positive constant $a$, which serves to amplify or attenuate the function as well as alter its shape.

@@

%For the remaining equations of this section, the only derivatives taken are with respect to $K_1$ for the similarity between targets $1$ and $2$ for simplicity; taking derivatives with respect other $K_i$ values are identical except for subscripts.

>>>>

\title{\LARGE \bf
%Recursive Kalman-Mahanobis JPDAF Minimization to avoid Coalescence of Estimates in Close Proximity
Optimal Joint Probabilistic Data Association Filter\\ Avoiding Coalescence in Close Proximity }
\author{Evan Kaufman, Thomas Alan Lovell, and Taeyoung Lee$^*$
 \thanks{Evan Kaufman and Taeyoung Lee are with Department of Aerospace Engineering, George Washington University, Washington, DC. Email: {\tt\footnotesize \{evankaufman, tylee\}@gwu.edu }}
\thanks{Thomas Alan Lovell is a Research Aerospace Engineer at the Space Vehicles Directorate, Air Force Research Lab (AFRL), Albuquerque, NM. Email: {\tt\footnotesize afrl.rvsv@kirtland.af.mil }}
\thanks{$^*$This research has been supported in part by NSF under the grants CMMI-1243000 (transferred from 1029551), CMMI-1335008, and CNS-1337722.}}

@@

\begin{abstract}
This paper deals with an estimation problem where a known number of objects in close proximity are observed but the measurement originations are uncertain. It is well known that joint probabilistic data association filters (JPDAF) are effective in handing uncertain measurement originations with clutter, but they are prone to estimation coalescence, particularly when close neighboring objects share measurements. This paper proposes a Coalescence Avoiding Optimal JPDAF (C-JPDAF) that minimizes the weighted sum of the posterior uncertainty and a measure of similarity between estimated probability densities. The proposed approach has simpler structures than other coalescence avoiding approaches based on pruning, while exhibiting excellent filtering performance for objects in close proximity with crossing tracks. These are illustrated by a numerical example of two satellites on crossing orbits around the Earth.
%The algorithm is derived and explained, involving a higher computational cost that the JPDAF, but not high enough to prevent the possibility real-time implementation. A numerical example demonstrates how the C-JPDAF is able to maintain the correct trajectories of slowly crossing estimates whereas the JPDAF is not. The results show that the Kalman gain is an effective initial guess for the C-JPDAF, and we discuss the circumstances that warrant the algorithm's use.
\end{abstract}

@@

Data association is a heavily studied field with many applications in estimation when measurements are not necessarily originating from a single object.
We consider applications wherein multiple objects of interest enter the field of view of a sensor; however, the measurement origin is unknown.
To properly track these objects, we require estimation techniques to associate objects with measurements.
When the objects are in very close proximity, the association uncertainty grows, and an effective algorithm is necessary to maintain close estimations of the objects.

A variety of data association techniques are considered for close-proximity trajectories with varying performance.
Some approaches such as multiple hypothesis tracking (MHT) and probability hypothesis density (PHD) techniques involve a high computational load, especially when objects are in close proximity, making real-time implementation more difficult~\cite{MHT1},~\cite{PHD1}, and~\cite{PHD2}.
Many other techniques may involve the Kalman filter (KF) or extended KF (EKF), which are well studied and provide a framework for recursive data association techniques that are much easier to implement in real-time.
A common heuristic approach is known as the nearest neighbor filter (NNF), which is a simple algorithm that only updates estimates for measurements with the closest square Mahalnobis distance, updating other objects only with their predictions~\cite{NN2}.
This is considered a \emph{hard decision} in~\cite{JPDAF1}, or that every measurement update receives full weighting; if the decision is incorrect, these measurement updates can result in detrimental effects to the associations of the estimates, so this technique is avoided in the analysis of this paper.
Alternatively, some approaches calculate the minimum mean square error (MMSE) of the estimates and their associated uncertainty.
The probabilistic data association (PDA) technique is effective in tracking a single object because it updates with a \emph{soft decision}; in particular, this approach updates provides a weighting from a likelihood of measurement association.

The joint PDA (JPDA) is an extension of the PDA to incorporate multiple objects~\cite{JPDAF1},~\cite{TrackDataAssoc}.
The JPDA filter (JPDAF) is particularly advantageous in multi-object scenarios because when objects share measurements, the soft decisions prevent loss of information, which occurs with hard decisions.
However, when neighboring objects share measurements, the estimates are subject to coalescence.

@@

@@

This section describes the dynamics of objects and the measurement model considered in this paper, and a filtering problem is formulated.

% Equations of motion
\subsection{Dynamics of Objects and Measurements}

The dynamics of each object is modeled as a linear stochastic discrete-time system belonging to the set $S$ such that
\begin{align}
S=\left\{i=1,2,...n\right\}
\end{align}
where $n$ is the number of objects.
The equations of motion for the $i$-th system are described by
\begin{align}
x_{i_{k+1}} & = A_{i_k} x_{i_k} + w_{i_k},\label{eqn:xkp}\\
z_{i_k} & = H_{i_k} x_{i_k} + v_{i_k},
\end{align}
where $x_{i_k}\in\Re^n$ is the state vector, $z_{i_k}\in\Re^m$ is the output vector, and  the matrices $A_{i_k}\in\Re^{n\times n}$ and $H_{i_k}\in\Re^{m\times n}$ describe system dynamics and outputs. The process noise and the measurement noise are denoted by $w_{i_k}\in\Re^n$ and $v_{i_k}\in\Re^m$, respectively, and it is assumed that they are zero-mean, mutually independent white, Gaussian noise sequences with known covariance matrices $Q_{i_k}\in\Re^{n\times n}$ and $R_{i_k}\in\Re^{m\times m}$, respectively, i.e.,
\begin{align}
w_{i_k} \sim \mathcal{N}[0,Q_{i_k}],\quad
v_{i_k} \sim \mathcal{N}[0,R_{i_k}].
\end{align}

@@

To demonstrate the main idea of the proposed data association filter concisely, it is assumed that there are two objects, i.e., $i\in\{1,2\}$. But, the results of this paper are readily generalized to arbitrary number of systems provided the number of objects is known.

@@

The following assumptions are made on the measurement origination, considering the case where two object are in close proximity. First, it is assumed that there is only a single measurement at each time in the region of close proximity. Secondly, we assume that this measurement originates from either one of the objects and it is not from other sources such as clutter. Also, the case when neither object is measured is not considered. Like the JPDA, all objects are assumed to fall inside the validation gate. The measurement origination between objects is random, unknown, and equally likely.

More explicitly, let $\Theta_i$ be the event that the measurement originates from the $i$-th object, for $i\in\{1,2\}$. According to the above assumptions, we have
\begin{align}
P(\Theta_1\cup \Theta_2)&=1,\quad
P(\Theta_1\cap \Theta_2)=0,\\
P(\Theta_1)&=P(\Theta_2)=0.5\label{eqn:MeaOrig}
\end{align}
where the equal probability of detection is due to their close proximity.

@@

A filtering problem is formulated as recursively updating the estimated state of each object and its covariance, namely $(\hat x_{i_k}, P_{i_k})$ based on the above assumptions given by \refeqn{xkp}--\refeqn{MeaOrig}. In particular, we wish to avoid track coalescence when two objects are in close proximity.

@@

Joint probabilistic data association filter is a suboptimal Bayesian filter for multiple objects where the probabilities of association are computed for the latest set of measurements only~\cite{TrackDataAssoc}. This section summarizes the approaches of JPDAF.

\subsection{Flow Update}
Similar to Kalman filters, the JPDAF is composed of a flow update and a measurement update. During the flow update (or prediction step), the estimated state $\hat x_{i_k}$ and its covariance $P_{i_k}$ of each object are updated as in the standard filter as follows:
\begin{gather}
\hat x_{i_{k}} = A_{i_{k-1}} \hat x_{i_{k-1}},\\
P_{i_{k}} = A_{i_{k-1}} P_{i_{k-1}} A_{i_{k-1}}^T + Q_{i_{k-1}}.
\end{gather}
These are initialized by \refeqn{xi0}, and they are repeated between measurements.

@@

Next, we consider the measurement update step. Let  the a priori value of a variable and its a posteriori value be denoted by the superscript $-$ and $+$, respectively. For a given measurement $z_{k}$, its measurement residual or innovation for the $i$-th object is given by
\begin{align*}
e_{i_k} = z_k - z_{i_{k|k-1}},
\end{align*}
where $z_{i_{k|k-1}}$ is the predicted measurement given by
\begin{align}
z_{i_{k|k-1}} = H_{i_k} \hat x_{i_k}^-.
\end{align}
The innovation covariance $S_{i_k}$ is
\begin{align}
S_{i_k}=H_{i_k}P_{i_k}^{-}H_{i_k}^T+R_{i_k}.
\end{align}

@@

The resulting a posteriori covariance is given by
\begin{align}
\label{KalCov}
%P^+_{i_k}=&P^-_{i_k}-\beta_{i_k}K_{i_k}S_{i_k}K_{i_k}^T.
P^+_{i_k}=&P^-_{i_k}-\beta_i[K_iH_iP_i^-+P_i^-H_i^TK_i^T-K_iS_{i_k}K_i^T].
\end{align}
(see Appendix for derivation of (\ref{KalCov})).

@@

The joint probabilistic data association filter described in the previous section is effective in handling clutter or missed detection of multiple objects. However, it is prone to coalescing estimates, especially with objects in close-proximity. Here, we present a coalescence-avoiding optimal JPDAF, hereafter C-JPDAF for short, to avoid coalescence of the estimates. The main idea is choosing the estimator gain such that a weighted sum of the size of uncertainty and a measure of similarity is minimized.

@@

For two Gaussian probability density functions, $f_1(x)$ and $f_2(x)$, Matusita's measure is defined as
\begin{align*}
\zeta = \int \sqrt{f_1(x)f_2(x)}dx,
\end{align*}
which is between 0 and 1, and it measures the similarity between two densities~\cite{Coal_k}.

From~\cite{Coal_k}, using the assumption that the a posteriori states $\hat x_1^+$ and $\hat x_2^+$ are Gaussian, the Matusita's measure between two objects can be written as
\begin{align}
\zeta=\zeta_1\zeta_2,
\end{align}
where
\begin{align}
\label{Q}
\zeta_1=&\frac{2^\frac{n}{2}|P_1^+|^{\frac{1}{4}}|P_2^+|^{\frac{1}{4}}}{|P_1^++P_2^+|^{\frac{1}{2}}},
\end{align}
\begin{align}
\label{R}
\zeta_2=&\exp{\left\{-\frac{1}{4}(\hat x^+_1-\hat x^+_2)^T(P_1^++P_2^+)^{-1}(\hat x^+_1-\hat x^+_2)\right\}}.
\end{align}
Here $\zeta_1$ measures the differences in the covariance matrices and $\zeta_2$ represents the spread in the means.
	% Introduce the definition of M-measure
	% Introduce the definition of Bhattacharyya distance

@@

\begin{figure}
\setlength{\unitlength}{0.1\columnwidth}
\centerline{\footnotesize\selectfont
\begin{picture}(8.5,7.3)(-0.5,-0.8)
\put(-0.5,3){\rotatebox{90}{Cost}}
\put(0,0){\includegraphics[width=0.8\columnwidth]{ECC14_fig1.pdf}}
\put(6.2,0.2){\shortstack[c]{Uncertainty\\ cost: $J_P$}}
\put(6.2,2.8){\shortstack[c]{Similarity\\ cost: $J_S$}}
\put(5.7,5.2){\shortstack[c]{Weighted sum:\\ $J=J_P+cJ_S$}}
\put(4.98,0.78){\circle*{0.1}}
\put(2.48,1.57){\circle*{0.1}}
\put(5.0,-0.3){$K_{JPDA}$}
\put(2.5,-0.3){$K$}
\put(3.1,-0.8){Estimator gain}
\end{picture}
}
\caption{Illustration of optimal coalescence avoidance: several costs are illustrated with respect to the estimator gain $K$ (red: uncertainty cost $J_P$, blue: similarity cost $J_S$, black: weighted sum). The estimator gain $K_{JPDA}$ of JPDA is selected to minimize the uncertainty cost. In the proposed approach, the estimator gain $K$ is chosen such that the weighted sum of the uncertainty cost and the similarity cost is minimized. In short, at the expense of increased uncertainty at a single step, the proposed approach prevents coalescence. The increased uncertainty at each step is rewarded by reducing the overall estimation error drastically by maintaining correct data association throughout crossing tracks in close proximity.}
%The cost functions of object 1 are examined under the variation of a single element of $K_1$. The resulting cost function (black) is minimized slightly to the right of the uncertainty cost function (blue). Note that the total cost when the Kalman gain is applied does not lie on the total cost curve because other elements of this gain that are not optimal. In Kalman filtering applications, including the JPDAF, only the uncertainty cost function is minimized.}
\label{CostTrends}
\end{figure}

More explicitly, the uncertainty cost $J_P$ is defined as the sum of the trace of each a posteriori covariance:
\begin{align}
J_P=\tr{P^+_1}+\tr{P^+_2},\label{eqn:JP}
\end{align}
where $P^+_{i_k}$ is obtained by (\ref{KalCov}). The similarity cost is chosen as the second part of the Matusita's measure that represent the weighted-spread of the mean values:
\begin{align}
J_S&=\exp (-au),\\
u & = (\hat x^+_1-\hat x^+_2)^T(P^+_{1}+P^+_{2})^{-1}(\hat x^+_1-\hat x^+_2).\label{eqn:u}
\end{align}
for positive constant $a$, which serves to amplify or attenuate the function as well as alter its shape.

@@

%For the remaining equations of this section, the only derivatives taken are with respect to $K_1$ for the similarity between objects $1$ and $2$ for simplicity; taking derivatives with respect other $K_i$ values are identical except for subscripts.

Next, we derive the derivative of each cost. For simplicity, derivatives with respect to the first gain $K_1$ are presented, and derivatives with respect to $K_2$ can be obtained in the same way. By substituting (\ref{KalCov}) into \refeqn{JP} and using the property $\frac{\partial}{\partial X}\tr{XYX^T}=2XY$ for any matrix $X$ and any symmetric matrix $Y$, we obtain
\begin{align}
\label{CostP}
\frac{\partial J_{P,1}}{\partial K_{1}}&=2\beta_1({K_1S_1-P_1^-H_1^T}).
\end{align}
%
%To appropriately define the similarity cost, we only consider the $R$ term from Equation \ref{R} because coalescence is well known to occur when estimates are within close proximity. For simplicity, we define ${P^+_{12}}^{-1}$ as
%\begin{align}
%{P^+_{12}}^{-1}=(P_1^++P_2^+)^{-1}
%\end{align}
%and define define $u$ as
Substituting (\ref{KalEst}) and (\ref{KalCov}) into \refeqn{u}, and rearranging, 
\begin{align}
u%=&(\hat x^+_1-\hat x^+_2)^T{P^+_{12}}^{-1}(\hat x^+_1-\hat x^+_2)\\
=&\{\hat x_1^{-T}{P^+_{12}}^{-1}\hat x_1^-
-2\hat x_1^{-T}{P^+_{12}}^{-1}\hat x_2^-\nonumber\\
&+2\beta_1(\hat x_1^{-}-\hat x_2^{-})^T{P^+_{12}}^{-1}K_1e_1
+\hat x_2^{-T}{P^+_{12}}^{-1}\hat x_2^-\nonumber\\
&+2\beta_2(\hat x_2^{-}-\hat x_1^{-})^T{P^+_{12}}^{-1}K_2e_2
+\beta_1^2e_1^TK_1^T{P^+_{12}}^{-1}K_1e_1\nonumber\\
&-2\beta_1\beta_2e_2^TK_2^T{P^+_{12}}^{-1}K_1e_1+\beta_2^2e_2^TK_2^T{P^+_{12}}^{-1}K_2e_2\},
\end{align}
where ${P^+_{12}}^{-1}=(P_1^++P_2^+)^{-1}$.
